 

### 2023-06-26 markdown/discussion.Rmd
tried to fix clusters

km.final <- kmeans(protein_matrix_t, 2)

@@

dimred_pca$cluster <- scp$cluster$km.final.cluster

ggplot(dimred_pca, aes(x=PC1, 
                       y=PC2,
                       shape = scp$SampleType)) +
  geom_point() +
  guides(color="none", shape="none") +
  stat_ellipse(data=dimred_pca, aes(fill=factor(cluster)),
               geom="polygon", alpha=0.2, level=0.9, type="t", linetype=2, show.legend = F) +
  coord_fixed() +
  labs(title=paste("Principle Components with", 2, "clusters"))

>>>>

#optimal_clusters <- 4

km.final <- kmeans(protein_matrix_t, optimal_clusters)

@@

dimred_pca$cluster <- factor(scp$cluster$km.final.cluster) 
dimred_pca$SampleType <- scp$SampleType

ggplot(dimred_pca, aes(x=PC1, 
                       y=PC2,
                       shape = SampleType,
                       color=cluster)) +
  geom_point() +
  guides(color="none", shape="none") +
  labs(title=paste("Principle Components with", optimal_clusters, "clusters")) +
  stat_ellipse(data = dimred_pca, 
               aes(fill = cluster),
               geom = "polygon", 
               alpha = 0.2, 
               level = 0.9, 
               type = "norm", 
               linetype = 2, 
               show.legend = F,
               na.rm = T) +
  coord_fixed()

# ggplot(dimred_pca, aes(x=PC1, 
#                        y=PC2,
#                        shape = SampleType
#                        )) +
#   geom_mark_ellipse(aes(fill=cluster, color=cluster)) +
#   geom_point()
```
